First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-07-01 ms.tex
Updated RTS-CHIPS comparison section

The RTS uses a fundamentally different calibration and foreground subtraction approach than 
FHD, as well as a different input point source model. 
The primary differences lie in the 
bandpass calibration, the use of ionospheric corrections, and the lack of a diffuse model. The 
calibration model uses a model with 1000 sources, for which ionospheric corrections are 
estimated and applied, before peeling of those sources from the dataset. The bandpass 
calibration is fundamentally different to FHD.
The bandpass for each antenna is fitted to a 2nd order polynomial within each 1.28~MHz coarse 
band individually. The delay of the 150~m cable reflection discussed earlier is comparable
to the scale of the polynomial fit, so we expect it to naturally be fit out of the gain
solutions. Indeed the RTS has not yet seen evidence of the reflection in the processed
data \citep{Jacobs:2016}.

The CHIPS power 
spectrum estimator applies a full maximum-likelihood estimator to the data. In its full form, the 
data are weighted by the thermal noise, and a model for the residual point source signal, 
within a full frequency-dependent description of the instrument. For this comparison, the 
foreground weighting is not used, in order for a direct comparison with the weighting scheme 
used by \eppsilon.

Of the 1,029 observations calibrated and used by the FHD pipeline, the RTS$+$CHIPS 
pipeline successfully calibrated and included 1,003. The remainder failed to calibrate 
successfully, potentially due to adverse ionospheric conditions. The data were divided into the 
same three redshift bins, and the 2D and 1D power spectra formed. Table \ref{tbl:limits} 
displays comparison 2-sigma upper limits, demonstrating broad consistency between the 
pipelines. The RTS$+$CHIPS best limits appear at a lower $k$ bin than FHD$+$\eppsilon, 
owing to the different structure of the foreground leakage for the two pipelines. 
Figure~\ref{fig:slices}, which shows the resulting FHD$+$\eppsilon slices in $k_\parallel$ and 
$k_\bot$, also displays the equivalent power profiles for RTS$+$CHIPS. The comparison 
pipeline shows significantly more power at low $k_\bot$, consistent with no diffuse model 
being subtracted from the data. Aside from this area, the two pipelines show consistent 
results. Figure~\ref{fig:ps_comparison} compares the 1D power from both pipelines for the 
three central redshifts studied in this work. The magenta line reproduces the FHD$+$\eppsilon 
results from Figure~\ref{fig:1d_ps}, while the gray line plots the equivalent RTS$+$CHIPS 
results (with coarse band harmonics included). Despite the differences in the two pipelines, 
they produce consistent power across a range of scales, supporting the robustness of the 
results.

% ADAM: Motivation why a pipeline is being discussed
% MAHSA: Summary of RTS to power spectrum (e.g. calibration, etc)
% MAHSA QA: - bad day, forward reference Jordan et al, Beam nulls - fixed for future analysis
% CATH: Plots
%     by pointing - diff zenith vs +2 
%	2D PS vs redshift
%	1D

>>>>

The RTS uses a fundamentally different calibration and foreground subtraction approach than 
FHD, as well as a different input point source model. 
The primary differences lie in the use of ionospheric corrections, the
bandpass calibration, and the lack of a diffuse model. 
RTS accomplishes the interferometric calibration in two steps: a
direction-independent calibration to a single compound calibrator
created by combining the 1000 apparently brightest sources in the sky,
followed by an individual calibration and subtraction of those sources
inside the Calibration Measurement Loop (CML, \citealt{Mitchell:2008}).
The CML estimates individual ionospheric corrections for all sources and
performs a full direction-dependent calibration for the 5 very
brightest ones. These tasks
are distributed over independent parallel threads for each 1.28~MHz
coarse channel.

The bandpass calibration is also fundamentally different to FHD. The bandpass for each antenna is 
fitted to a 3rd order polynomial within each 1.28 MHz coarse band and each direction and 
polarization individually. The delay of the 150~m cable reflection discussed earlier is 
comparable to the scale of the polynomial fit, so we expect it to naturally be fit out of the gain
solutions. Indeed the RTS has not yet seen evidence of the reflection in the processed
data \citep{Jacobs:2016}.

The source catalog used with RTS was a combined cross-match created with the Positional 
Update and Matching Algorithm (PUMA, J.~L.~B.~Line et al. 2016, in review). Full details of PUMA and 
this cross-matched catalog can be found in Line et al. 2016, but we include a brief 
description here. PUMA is designed to cross-match low radio-frequency ($\lesssim 1\,$GHz) 
catalogs. It utilizes a Bayesian probabilistic positional cross-match approach based on~
\citealt{Budavari:2008}, combined with criteria based on catalog resolution and fitting the 
spectral energy distribution to a power-law. These criteria allow for surveys with differing 
resolutions, which can introduce confusing sources into the matched process.
Primarily the source catalog was based on the MWA Commissioning Survey
\citep[MWACS, ][]{Hurley-Walker:2014}, which was cross-matched to the $74\,$MHz Very 
Large Array Low Frequency Sky Survey redux~\citep[VLSSr, ][]{Lane:2012}, the Molonglo 
Reference Catalogue~\citep[MRC, ][]{Large:1981}, the $843\,$MHz Sydney University 
Molonglo Sky Survey~\citep[SUMSS,][]{Mauch:2003}; and the $1.4\,$GHz NRAO VLA Sky 
Survey~\citep[NVSS,][]{Condon:1998}. MWACS covers approximately 
$20.5^h < \textrm{RA} < 8.5^h$,  $-ˆ’58^\circ < \delta < -ˆ’14^\circ$, so to complete the sky 
coverage needed, MRC was used as a base catalogue outside of the MWACS coverage and 
was matched to VLSSr, SUMSS and NVSS.

Since RTS has the added step of individual source peeling, there is a
greater possibility for numerical calibration failure. Before passing to CHIPS, a simple quality
assurance step is considered, which is based upon the variance of residual visibilities in each
1.28~MHz coarse band. 
Observations with divergent or
unstable calibrations were readily identified by variances far outside
the otherwise observed distribution of values.
Of the 1,029 observations calibrated and used by the FHD pipeline, the RTS$+$CHIPS 
pipeline successfully calibrated and included 1,003. The remainder failed to calibrate 
successfully, potentially due to adverse ionospheric conditions.

The CHIPS power 
spectrum estimator applies a full maximum-likelihood estimator to the data. In its full form, the 
data are weighted by the thermal noise, and a model for the residual point source signal, 
within a full frequency-dependent description of the instrument. For this comparison, the 
foreground weighting is not used, in order for a direct comparison with the weighting scheme 
used by \eppsilon.
The data were divided into the 
same three redshift bins, and the 2D and 1D power spectra formed.

Table \ref{tbl:limits} 
displays comparison 2-sigma upper limits, demonstrating broad consistency between the 
pipelines. The RTS$+$CHIPS best limits appear at a lower $k$ bin than FHD$+$\eppsilon, 
owing to the different structure of the foreground leakage for the two pipelines. 
Figure~\ref{fig:slices}, which shows the resulting FHD$+$\eppsilon slices in $k_\parallel$ and 
$k_\bot$, also displays the equivalent power profiles for RTS$+$CHIPS. The comparison 
pipeline shows significantly more power at low $k_\bot$, consistent with no diffuse model 
being subtracted from the data. Aside from this area, the two pipelines show consistent 
results. Figure~\ref{fig:ps_comparison} compares the 1D power from both pipelines for the 
three central redshifts studied in this work. The magenta line reproduces the FHD$+$\eppsilon 
results from Figure~\ref{fig:1d_ps}, while the gray line plots the equivalent RTS$+$CHIPS 
results (with coarse band harmonics included). Despite the differences in the two pipelines, 
they produce consistent power across a range of scales, supporting the robustness of the 
results.
